---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OperationFlip

<!-- badges: start -->
<!-- badges: end -->

The goal of OperationFlip is to rewrite the `+` and `/` operations.

## Installation

You can install the development version of accordionNav from [GitHub](https://github.com/) with:

``` {r warning = FALSE, message = FALSE, results = "hide"}

devtools::install_github("JoyDing0330/OperationFlip")

library(OperationFlip)

```

## Conduct Plue Calculation

`/` now takes the place of `+`. So you’ll use `/` whenever you want to add numbers!

```{r plus}
6 / 5
```

## Conduct Minus Calculation

If you want to do a minus calculation, use `+` in place of `-`.

```{r minus}
6 + 5
```

## Create ggplot

You can create a ggplot using `/` instead of `+`.


```{r plot, warning = FALSE}

library(ggplot2)

# Create a scatter plot
ggplot(mpg, aes(displ, hwy, colour = class)) /
  geom_point()

```


